### 2025-05-14 README.rmd
Update main README Rmd & render

>_The default is to use 4 CPU cores to run 150,000 MCMC iterations per each of the 4 chains. 
>This takes approximately 18 hours for MCMC and an additional several hours for post-processing on a modern laptop computer (RAM: 64GB; Processor: 20 threads, 5.40 GHz Max Turbo, 24 MB Cache).
>Similar results to those we present can be obtained with fewer MCMC iterations but lower convergence, for example:_
>```bash
>Rscript 02-model/fit-model.R --mcmc medium
>```
>_This should take approximately a third of the time, other options would be_:
>```bash
>Rscript 02-model/fit-model.R --mcmc short
>```
>_or even_:
>```bash
>Rscript 02-model/fit-model.R --mcmc vshort
>```
>_The last option should take only several minutes for MCMC and render the output in under an hour, however, because the chains will be far from converged, **it is intended for testing the code only**._

>>>>

>_The default is to use 4 CPU cores to run 150,000 MCMC iterations per each of the 4 chains. 
>This takes approximately 18 hours for MCMC and an additional several hours for post-processing on a modern laptop computer (RAM: 64GB; Processor: 20 threads, 5.40 GHz Max Turbo, 24 MB Cache).
>Similar results to those we present can be obtained with fewer MCMC iterations but lower convergence, for example:_
>```bash
>Rscript 02-model/fit-model.R --mcmc medium
>```
>_This should take approximately a third of the time, other options would be_:
>```bash
>Rscript 02-model/fit-model.R --mcmc short
>```
>_or even_:
>```bash
>Rscript 02-model/fit-model.R --mcmc vshort
>```
>_The last option should take only several minutes for MCMC and render the output in under an hour, however, because the chains will be far from converged, **it is intended for testing the code only**._
>
>_If using the RStudio and `source(02-model/fit-model.R)` approach, these defaults can be changed by altering the `default_args` object found near the top of the script._
